---
title: "GARCH"
author: "Raphael Tang"
date: "10/15/2021"
output: pdf_document
---

Loading packages
```{r}
library(quantmod)
library(rugarch)
library(rmgarch)
library(vars)
library(zoo)
library(tidyverse)
library(mFilter)
library(tseries)
library(TSstudio)
library(forecast)
library(urca)
```

Getting the data
```{r}
startDate = as.Date("2007-01-01") #Specify period of time we are interested in
endDate = as.Date("2018-04-30")

Returns <- ts(Proposal_1_$Returns, start = c(2000,1,30), frequency = 52)

#Str command is to make the object a time series
str(Returns)

#Normal graph
autoplot(Returns)


```

Diagnostics
```{r}
#Augmented dickey fuller
adf.test(Returns)


#Test for ARCH effects 
arch.test(Returns, lags.multi = 9, multivariate.only = TRUE)

#Test for normality of residuals
normality.test(Returns, multivariate.only = TRUE)
```

Further specification options
sGARCH under the variance model changes the standard GARCH order
Mean model changes the ARMA fitting
Distribution model sees the distribution of epsilon
```{r}
garchspec <- ugarchspec(mean.model = list(armaOrder=c(1,1), include.mean = TRUE), variance.model = list(model="sGARCH", garchOrder = c(1,1)), distribution.model="norm")

garchspec
```

Lag order
```{r}
#AIC
infocriteria(garchspec)
#BIC
BIC(garchspec)

```

Estimating the model
```{r}
garchfit <-  ugarchfit(spec = garchspec, data = rIBM)
garchfit
```

Estimated coefficients and residuals
```{r}
#For estimated coefficients
garchcoef <- coef(garchfit)
#Unconditional variance
garchuncvar <- uncvariance(garchfit)
#Predicted mean
garchmean <- fitted(garchfit)
#Volatility (predicted)
garchvol <- sigma(garchfit)
```

Maximum likelihood estimation
```{r}
MLE <- likelihood(garchfit)
```

Conditional variance graph
```{r}
plot(ug_res2, type = "l")
lines(ug_var, col = "green")
garchvol <- sigma(ugarchfit)
plot(garchvol)
```

Forecasting
```{r}
ugfore <- ugarchforecast(ugfit, n.ahead = 10)
ugfore

#Sigma forecast
ug_f <- ugfore@forecast$sigmaFor
plot(ug_f, type = "l")
```

Note that the volatility is the square root of the conditional variance.
